MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
small fixups

One might describe our final piece, \emph{Digital Nightmare}, as an unrelenting flood of almost patternless musical information.
This characteristic emerges from some simplifications in design choices that a later vernon of our process would look to address.
Here we present a list of such areas and possible solutions.

@@

\item Each instrument plays a note during every musical time unit
  (beat). This results in constant note information without any space
  for the listener to "catch up".  Darker colors below some threshold
  of brightness could all be translated into musical rests.

\item Each note played last only one beat, i.e quarter notes are the
  only length note used.  Consecutive image regions with similar
  colors could be "strung together" cause some instruments to play
  longer notes.

\item Late on in the process, we moved from saturation mapping to
  velocity to choosing a fixed velocity of 127.  We found that
  velocity dynamics were not so perceptible with the degree of musical
  production we were willing to invest.  Spending more time in the
  post-processing phase and focusing on musical dynamics such as
  volume, panning, etc could improve the contribution of velocity to a
  musical piece.

>>>>

One might describe our final piece, \emph{Digital Nightmare}, as an unrelenting flood of almost patternless musical information.
This characteristic emerges from some simplifications in design choices that a later version of our process would look to address.
Here we present a list of such areas and possible solutions.

@@

\item Each instrument plays a note during every musical time unit
  (beat). This results in constant note information without any space
  for the listener to ``catch up.''  Darker colors below some
  threshold of brightness could all be translated into musical rests.

\item Each note played last only one beat, i.e quarter notes are the
  only length note used.  Consecutive image regions with similar
  colors could be ``strung together'' cause some instruments to play
  longer notes.

\item Late on in the process, we moved from saturation mapping to
  velocity to choosing a fixed velocity of $127$.  We found that
  velocity dynamics were not so perceptible with the degree of musical
  production we were willing to invest.  Spending more time in the
  post-processing phase and focusing on musical dynamics such as
  volume, panning, etc could improve the contribution of velocity to a
  musical piece.
